Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
minor

We wrote our main control program, classify.py, so that it can choose either the
\naive{} Bayes or decision tree classifier and any combination of  features. On
top of this we wrote bash scripts that automated looping through every
combination of classifiers and features, along with porting the results directly
into the scorer.  \verb+classify.py+ includes a help switch -h, that explains
the switches that control the different classifiers and features along with any
additional parameters that a certain feature might support (for example,
collocation has a window size parameter which defaults to 0) Performance was
excellent for most of the features, allowing us to typically run all of the
words in the test set through every combination a classifier and feature set in
under an hour, although dependency parsing was slow (The number of runs can get
quite high when you factor in several parameters per feature, not just on/off)

>>>>

We wrote our main control program, classify.py, so that it can choose either the
\naive{} Bayes or decision tree classifier and any combination of  features. On
top of this we wrote bash scripts that automated looping through every
combination of classifiers and features, along with porting the results directly
into the scorer.  \verb+classify.py+ includes a help switch \verb+-h+, that
explains the switches that control the different classifiers and features along
with any additional parameters that a certain feature might support (for
example, collocation has a window size parameter which defaults to 0)
Performance was excellent for most of the features, allowing us to typically run
all of the words in the test set through every combination a classifier and
feature set in under an hour, although dependency parsing was slow (The number
of runs can get quite high when you factor in several parameters per feature,
not just on/off)
